Evaluate PEER in each cohort and brain region

### 2021-03-15 combined_analysis/eval_resid_in_each.Rmd
upload correct cell type

    # PEER_setNmax_iterations(model, 2)
    PEER_setNk(model,50)

@@

    # upload observed expression
    file = paste0('geneExpr_',gsub(" ", '', gsub("-", "_", datID)), '_', CT,".RDS")
    storeData( geneExpr, file, paste0(datID, " Observed expression", ' - ', CT))

    # upload covariate matrix
    file = paste0('covariateMatrix_',gsub(" ", '', gsub("-", "_", datID)), '_', CT, ".RDS")
    storeData( cov_matrix, file, paste0(datID, " Covariates for QTL analysis", ' - ' , CT))

    # upload latent variables
    file = paste0('PEER_',gsub(" ", '', gsub("-", "_", datID)), '_', CT, ".RDS")
    storeData( latentVariables, file, paste0(datID, " Latent variables for QTL analysis", ' - ', CT))
  }
}
```

>>>>

    # # PEER_setNmax_iterations(model, 2)
    PEER_setNk(model,50)

@@

    # upload observed expression
    file = paste0('geneExpr_',gsub(" ", '', gsub("-", "_", datID)), '_', CT,".RDS")
    storeData( geneExpr[,i,], file, paste0(datID, " Observed expression", ' - ', CT))

    # # upload covariate matrix
    file = paste0('covariateMatrix_',gsub(" ", '', gsub("-", "_", datID)), '_', CT, ".RDS")
    storeData( cov_matrix, file, paste0(datID, " Covariates for QTL analysis", ' - ' , CT))

    # # upload latent variables
    file = paste0('PEER_',gsub(" ", '', gsub("-", "_", datID)), '_', CT, ".RDS")
    storeData( latentVariables, file, paste0(datID, " Latent variables for QTL analysis", ' - ', CT))
  }
}
```
